---
title: "Zajęcia 1"
author: "Natalia"
date: "5 października 2016"
output: html_document
---
Dane o filmach.




```{r,message=FALSE,warning=FALSE}
summary(cars)
library("PogromcyDanych")
head(serialeIMDB)
x=table(serialeIMDB$serial)
sort(x)
y<-filter(serialeIMDB,serial=="Friends")
#dim(y)
#summary(y)
group_by(y,sezon)->z
v=summarize(z,srednia=mean(ocena),max(ocena))
desc(serialeIMDB$serial)

serialeIMDB %>% 
  group_by(serial) %>% 
  summarize(srednia=mean(ocena)) %>% 
  arrange(-srednia)

ggplot(y,aes(x=sezon,y=ocena))+geom_boxplot()

```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

#Zajęcia 2 19.10


R version 3.2.2 (2015-08-14) -- "Fire Safety"
Copyright (C) 2015 The R Foundation for Statistical Computing
Platform: x86_64-w64-mingw32/x64 (64-bit)

R is free software and comes with ABSOLUTELY NO WARRANTY.
You are welcome to redistribute it under certain conditions.
Type 'license()' or 'licence()' for distribution details.

R is a collaborative project with many contributors.
Type 'contributors()' for more information and
'citation()' on how to cite R or R packages in publications.

Type 'demo()' for some demos, 'help()' for on-line help, or
'help.start()' for an HTML browser interface to help.
Type 'q()' to quit R.

> install.packages("BetaBit")
Installing package into ‘C:/Users/nj332194/Documents/R/win-library/3.2’
(as ‘lib’ is unspecified)
trying URL 'https://cran.rstudio.com/bin/windows/contrib/3.2/BetaBit_1.3.zip'
Content type 'application/zip' length 3364314 bytes (3.2 MB)
downloaded 3.2 MB

package ‘BetaBit’ successfully unpacked and MD5 sums checked

The downloaded binary packages are in
	C:\Users\nj332194\AppData\Local\Temp\RtmpyuPxru\downloaded_packages
> library(BetaBit)

 _____     _                    _    _____ _ _      _____
| __  |___| |_ ___    ___ ___ _| |  | __  |_| |_   |   __|___ _____ ___ ___
| __ -| -_|  _| .'|  | .'|   | . |  | __ -| |  _|  |  |  | .'|     | -_|_ -|
|_____|___|_| |__,|  |__,|_|_|___|  |_____|_|_|    |_____|__,|_|_|_|___|___|

Choose your game. Just type the name of the selected game in the console.
It's a function so do not forget about parentheses!

1. proton()
2. frequon()
3. regression()

Warning message:
pakiet ‘BetaBit’ został zbudowany w wersji R 3.2.5 
> proton()
 _____ _          _____         _              _____
|_   _| |_ ___   |  _  |___ ___| |_ ___ ___   |   __|___ _____ ___
  | | |   | -_|  |   __|  _| . |  _| . |   |  |  |  | .'|     | -_|
  |_| |_|_|___|  |__|  |_| |___|_| |___|_|_|  |_____|__,|_|_|_|___|

Your goal is to find Slawomir Pietraszko's credentials for the Proton server.
This is the only way for Bit to find the secret plans of Pietraszko's laboratory.

Remember that at any time you may add `hint=TRUE` argument to the executed command in order to get additional suggestions.

Pietraszko uses a password which is very difficult to guess.
At first, try to hack an account of a person which is not as cautious as Pietraszko.

But who is the weakest point? Initial investigation suggests that John Insecure doesn't care about security and has an account on the Proton server. He may use a password which is easy to crack.
Let's attack his account first!

Problem 1: Find the login of John Insecure.

Bit has scrapped 'employees' data (names and logins) from the www web page of Technical University of Warsaw. The data is in the data.frame `employees`. 
Now, your task is to find John Insecure's login.
When you finally find out what John's login is, use `proton(action = "login", login="XYZ")` command, where XYZ is Insecure's login.
> table(BetaBit$employees)
Error in table(BetaBit$employees) : object 'BetaBit' not found
> head(employees)
    name  surname       login
1  Jorge  Patrick   j.patrick
2 Gerald     Long gerald.long
3 Javier  Mendoza   j.mendoza
4    Roy Johnston        rjoh
5  Annie    Keith annie.keith
6   Nora   Castro        ncas
> x=table(employees)
> y<-filter(employees,surname=="Insecure")
Error in filter(employees, surname == "Insecure") : 
  object 'surname' not found
In addition: Warning message:
In data.matrix(data) : NAs introduced by coercion
> y<-filter(employees,=="")
Error: unexpected '==' in "y<-filter(employees,=="
> library(dplyr)

Dołączanie pakietu: ‘dplyr’

Następujące obiekty zostały zakryte z ‘package:stats’:

    filter, lag

Następujące obiekty zostały zakryte z ‘package:base’:

    intersect, setdiff, setequal, union

Warning message:
pakiet ‘dplyr’ został zbudowany w wersji R 3.2.5 
> head(employees) 
    name  surname       login
1  Jorge  Patrick   j.patrick
2 Gerald     Long gerald.long
3 Javier  Mendoza   j.mendoza
4    Roy Johnston        rjoh
5  Annie    Keith annie.keith
6   Nora   Castro        ncas
> 
> filter(employees,surname == "Insecure")
  name  surname   login
1 John Insecure johnins
> proton(action = "login", login="johnins")
Congratulations! You have found out what John Insecure's login is!
It is highly likely that he uses some typical password.
Bit downloaded from the Internet a database with 1000 most commonly used passwords.
You can find this database in the `top1000passwords` vector.

Problem 2: Find John Insecure's password.

Use `proton(action = "login", login="XYZ", password="ABC")` command in order to log into the Proton server with the given credentials.
If the password is correct, you will get the following message:
`Success! User is logged in!`.
Otherwise you will get:
`Password or login is incorrect!`.
> head(top1000passwords)
[1] "123456"    "password"  "12345678"  "qwerty"    "123456789" "12345"    
> for(i in 1:1000){
+     proton(action = "login", login="johnins", password=top1000passwords[i])
+ }
Well done! This is the right password!
Bit used John Insecure's account in order to log into the Proton server.
It turns out that John has access to server logs.
Now, Bit wants to check from which workstation Pietraszko is frequently logging into the Proton server. Bit hopes that there will be some useful data.  

Logs are in the `logs` dataset. 
Consecutive columns contain information such as: who, when and from which computer logged into Proton.

Problem 3: Check from which server Pietraszko logs into the Proton server most often.

Use `proton(action = "server", host="XYZ")` command in order to learn more  about what can be found on the XYZ server.
The biggest chance to find something interesting is to find a server from which Pietraszko logs in the most often.








